Optimal strategies in mental rotation tasks

### 2013-05-13 man/final-project.tex
Clean up gold standard model section

\subsubsection{Gold standard}

For comparison, we compute a ``gold standard'' by evaluating $S(X_b,
X_R)$ at 360 values spaced evenly between $0$ and $2\pi$.

>>>>

\subsection{Gold standard model}

To compare the accuracy of other models' estimates of $Z$, we computed
a ``gold standard''\footnote{This only gives an accurate estimate of
  $Z$, which is itself an approximation, and is thus not necessarily
  the true value of the numerator in Equation \ref{eq:lh-ratio}.} by
evaluating $S(X_b, X_R)$ at 360 values of $R$ spaced evenly between
$0$ and $2\pi$.
